---
title: "IP"
author: "Maureen Gatu"
date: "26/08/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
memory.limit(size = 96000)
```
## Loading the Libraries
```{r load-packages, include=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
#install.packages("devtools")
library(devtools)
#install.packages("Hmisc")
library(Hmisc)
```

# Loading the Data
```{r}
#setting up the enviroment
getwd()

#locating the dataset
setwd("A:\\PROGRAMMING WITH R\\advert")

#Loading the dataset

advt <- read.csv('advertising.csv',sep = ',', header=TRUE)
```
## Preview the dataset
```{r}
#Preview the top of the dataset
head(advt)
```
```{r}
#Preview thr bottom of the dataset
tail(advt)
```

## Geting information about the dataset
```{r}
#Size  of the dataset
dim(advt)
```
Viewing the column names
```{r}
names(advt)
```
Checking the variables data types
```{r}
sapply(advt, class)
```
Checking the number of unique entries in each variable
```{r}
print(advt %>% summarise_all(n_distinct))
```
check the unique values in city
```{r}

```

# Data Cleaning

Change the TimeStamp variable to date type
```{r}

```

Checking for duplicates
```{r}
#Checking the duplicates using duplicated.data.frame() function
dim(advt)
table(duplicated.data.frame(advt))
print('The dataset has no duplicated records')
```
Check for misisng values
```{r}
print('Total size of our dataset')
print(dim(advt))
print('Number of row with missing entries')
null <- advt[!complete.cases(advt),]          #Give total number of rows with missing values
dim(null)
print(' ')
print('The dataset has no missing values')
```
Check for outliers using the boxplot
```{r}
#boxplot(advt$Daily.Time.Spent.on.Site,advt$Age,advt$Daily.Internet.Usage)
#boxplot(advt$Area.Income)
par(mfrow = c(2,2))
for (i in 1:4){
 boxplot(advt[,i], main = names(advt)[i], horizontal = TRUE) 
}
```
          There seems to be only one outlier in the area.income variable.
                        we view the outlier with using the min() 
```{r}
min(as.numeric(advt[,3]))
                          #Since the outlier is in regards to income, we choose to retain it.

``` 


# Exploratory Data Analysis


## Univariate Analysis

Descriptive stattistics of the dataset
```{r}
summary(advt)
```
Data distribution 
```{r}
describe(advt)
```

```{r}
par(mfrow = c(2,2))
for (i in 1:4){
  hist(advt[,i],main = names(advt)[i], xlab = NULL)
  
}
```



```{r}
head(advt)
```

Barplot
```{r}
table(advt$Male)
H <- table(advt$Male)
barplot(H,  col = 'darkgreen')
```
Clicked on vs not clicked on ads
```{r}
par()
table(advt$Clicked.on.Ad)
ads <- table(advt$Clicked.on.Ad)
barplot(ads,  col = 'darkgreen')
```
        175 ads were clicked on and 164 ads were not clicked on.

Separate between ads that were clicked on(1) and those that were not.
created a subset data of only ads that were clicked on to anlyze the target customers that click on the ads.
```{r}
clicked <- advt[advt$Clicked.on.Ad == 1,]
par(mfrow = c(2,2))
for (i in 1:4){
  hist(clicked[,i],main = names(clicked)[i], xlab = NULL)
  
}
```
Ads not clicked on
```{r}
not_clicked <- advt[advt$Clicked.on.Ad == 0,]
par(mfrow = c(2,2))
for (i in 1:4){
  hist(not_clicked[,i],main = names(not_clicked)[i], xlab = NULL)
  
}
```
Looking at the persons that clicked on the ad based on gender
Males who clicked on the add
```{r}
Male <- clicked[clicked$Male == 1,]
par(mfrow = c(2,2))
for (i in 1:4){
  hist(Male[,i],main = names(Male)[i], xlab = NULL)
  
}
```
Females that clicked on the ad
```{r}
Female <- clicked[clicked$Male == 0,]
par(mfrow = c(2,2))
for (i in 1:4){
  hist(Female[,i],main = names(Female)[i], xlab = NULL)
  
}
```
##### Time Spent on Site
```{r}
#Sort dataframe based on time spent on site variable
time_spent <- clicked[order(-clicked$Daily.Time.Spent.on.Site),]
head(time_spent$Ad.Topic.Line)
```
These are the ad topic line clicked among the people that spent the most amount of time on the site
```{r}
tail(time_spent$Ad.Topic.Line)
```
These are the ad topics clicked by persons that spent the least time on the site.

## Bivariate analysis
#### Correlation coefficients
```{r}
num <- advt[,1:4]
cor(num)
```

#### Scatter plots
```{r}
num <- advt[,1:4]
pairs(num, pch = 19)
```
Daily time spent on site, area.income and daily internet usage are all positvely correlated to each other.
Age has a negative correaltion to each of these three variable. The correlation between all variables is weak with the highest correlation beng between time spent on site and daily internet usage, with a correlation on 0.50.

